---
title: "IAD Analysis"
output: html_notebook
---

Some plots to consider for IAD Stakeholder Analysis Paper

Set working directory and load libraries
```{r}
knitr::opts_knit$set(echo = TRUE, root.dir = "~/Documents/GitHub/IAD_blockchain")
library(tidyverse)
library(ggplot2)
library(UESIplots)
library(ggrepel)
library(wesanderson)
library(ggdark) #devtools::install_github("nsgrantham/ggdark")

```

Load in data
```{r}
ghg <- read_csv("data/GCB2021v34_MtCO2_flat.csv")
unique(ghg$Country)

tl <- read_csv("data/climate_policy_timeline.csv")

# constituencies
orgs <- read_csv("Consolidated Data/aggregated_constituency_data.csv")
```
## Wrangling 
For a "timeline"-like plot of events against emissions, need to do a bit of wrangling 

## Global CO2 trend vs. Major Climate Policy Events
plot of global emissions vs. major climate events
```{r}
ghg_world <- ghg %>% filter(Country == "Global") %>% left_join(tl %>% filter(!event %in% c("US-China bilateral climate deal", "World Conference on Changing Atmosphere")), by=c("Year"="year")) %>% mutate(position=as.numeric(position))

cairo_pdf("plots/globalco2_timeline.pdf", width=12, height=6)
ghg_world %>% filter(Year >= 1950) %>%
ggplot(aes(x=Year, y=Total)) +
  geom_line(size=2, color="#CA0020") +
  geom_point(data=ghg_world[!is.na(ghg_world$event),], aes(x=Year, y=position), size=2)+
  geom_segment(data=ghg_world[!is.na(ghg_world$event),],aes(y=position, yend=Total, xend=Year), color="black", size=0.2)+  geom_text_repel(aes(x=Year, y=position, label=event),nudge_y=100, max.overlaps=20) +
  scale_x_continuous(breaks=seq(1950, 2020, 10))+
  #scale_y_continuous(expand = expansion(mult = c(0, 0.5)))+
  labs(x="", y="Total Emissions (MtCO2e)")+
  theme_classic() +
  theme(text=element_text(family="Myriad Pro", size=14))
dev.off()

# dark version

cairo_pdf("plots/globalco2_timeline_dark.pdf", width=12, height=6)
ghg_world %>% filter(Year >= 1950) %>%
ggplot(aes(x=Year, y=Total)) +
  geom_line(size=2, color="#CA0020") +
  geom_point(data=ghg_world[!is.na(ghg_world$event),], aes(x=Year, y=position), size=2)+
  geom_segment(data=ghg_world[!is.na(ghg_world$event),],aes(y=position, yend=Total, xend=Year), color="white", size=0.2)+  
  geom_text_repel(aes(x=Year, y=position, label=event),size=4, nudge_y=100, max.overlaps=20) +
  scale_x_continuous(breaks=seq(1950, 2020, 10))+
  #scale_y_continuous(expand = expansion(mult = c(0, 0.5)))+
  labs(x="", y="Total Annual Eemissions (MtCO2e)")+
   dark_theme_gray() +
  theme(text=element_text(family="Myriad Pro", size=14),
        axis.text=element_text(size=14)) 
dev.off()

```
### Constituents plot
Plot of constituents changing over time
```{r}
orgs_m <- orgs %>% pivot_longer(`Constituency - Business and Industry`:`Constituency - Youth`, names_to="Constituency", values_to="Value") %>% 
  mutate(Constituency=str_replace(Constituency, "Business and Industry.*$", "Business and Industry"),
         Constituency=str_replace(Constituency, "Environmental.*$", "Environmental NGO"),
         Constituency=str_replace(Constituency, "ENGO", "Environmental NGO"),
         Constituency=str_replace(Constituency, "Constituency - ", "")) %>%
  dplyr::select(-`not yet affiliated/no data`)

pal <- wes_palette("Rushmore1", 10, type="continuous")[c(1,3:10)]

cairo_pdf("plots/Constituencies_over_time_dark.pdf", width=8, height=6)
ggplot(orgs_m, aes(x=Conference, y=Value, fill=Constituency)) +
  geom_bar(position="stack", stat="identity") +
  scale_fill_manual(name="", values=pal)+
  labs(x="", y="Number of organizations")+
  dark_theme_gray() +
  theme(text=element_text(family="Myriad Pro", size=14, color="#ffffff"),
        axis.text=element_text(size=14))
dev.off()

cairo_pdf("plots/Constituencies_over_time_white.pdf")
ggplot(orgs_m, aes(x=Conference, y=Value, fill=Constituency)) +
  geom_bar(position="stack", stat="identity") +
  scale_fill_manual(name="", values=pal)+
  labs(x="", y="Number of organizations")+
  theme_classic() +
  theme(text=element_text(family="Myriad Pro", size=14),
        axis.text=element_text(size=14))
dev.off()


pal <- wes_palette("Rushmore1", 13, type="continuous")
# for class
orgs %>% pivot_longer(`Constituency - Business and Industry`:`Constituency - Youth`, names_to="Constituency", values_to="Value") %>% dplyr::select(-`not yet affiliated/no data`) %>%
ggplot(aes(x=Conference, y=Value, fill=Constituency)) +
  geom_bar(position="stack", stat="identity") +
  scale_fill_manual(name="", values=pal)+
  labs(x="", y="Number of organizations")+
  theme_classic() +
  theme(text=element_text(family="Myriad Pro", size=14))
```

